Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-30 manuscript.Rmd
Lots of updates. Big mess.

```{r plotSmallMultiples}
hIndex.df <- arrange(hIndex, desc(h5Median)) %>% select(title, h5Median)
hIndex.df$top10 <- NA
hIndex.df$top10[1:10] <- "Yes"
hIndex.df$top10[11:nrow(hIndex.df)] <- "No"
hIndex.df <- data.frame(hIndex.df)

sm.df <- left_join(n.so, n.yr) %>%
    group_by(title, year) %>%
    summarize(N = n()) %>%
    mutate(Overall.N = sum(N)) %>%
    ungroup() %>%
    arrange(desc(Overall.N), title)

sm.df <- full_join(sm.df, hIndex.df, by = "title") %>% 
    ungroup %>% 
    select(-h5Median)

@@

title <- sm.df %>% arrange(desc(Overall.N)) %>% distinct(title)

title.order <- title$title

sm.df$title2 <- factor(sm.df$title, levels = (title.order))

Overall.N <- distinct(sm.df, title)

@@

>>>>

```{r plotSmallMultiples}
sm.df <- left_join(n.so, n.yr) %>%
    group_by(title, year) %>%
    summarize(N = n()) %>%
    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
    ungroup() %>%
    arrange(desc(Overall.N), title) %>%
    rename(Year = year, Journal= title)

scopus.df <- read.csv("scopus.csv")

sm.scopus.merged <-full_join(sm.df, scopus.df, by = c("Journal", "Year")) %>%
    select(Year, Journal, N, Overall.N, Documents)

abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
abb$ID <- 1:nrow(abb)
sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal")

title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% distinct(Abbrev) %>% filter(!is.na(Abbrev))
title.order = title$Abbrev
sm.scopus.merged$title2 <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
Overall.N <- distinct(sm.scopus.merged, title2)

hd.df <- sm.scopus.merged %>% select(Year, Abbrev, Journal, N, Overall.N, title2)

scopus.plot.df <- sm.scopus.merged %>% select(Year, Abbrev, Journal, Documents,Overall.N)
scopus.plot.df$Documents <- ifelse(scopus.plot.df$Documents == 0, NA, scopus.plot.df$Documents)
scopus.plot.df <- scopus.plot.df[!is.na(scopus.plot.df$Documents), ]

xpos = rep(2000, 79)
ypos = rep(130, 79)

lab <- paste("N=", title$Overall.N, sep="")
Abbrev <- title$Abbrev

ldata <- data.frame(xpos, ypos, lab, Abbrev)

ggplot(hd.df,  aes(Year, N), group=1) + geom_line(colour="#e66101") +
    facet_wrap(~ Abbrev) + 
    geom_line(data = scopus.plot.df, aes(Year, Documents), colour="#5e3c99") + 
    theme_bw() +
    theme(legend.position = "bottom", 
    panel.grid.minor = element_blank(), 
    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
    geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3)

ggplot(sm.scopus.merged, aes(X, Documents)) + geom_point(aes(colour = Journal)) + 
    facet_wrap(~Year) +
    geom_smooth()

cor(sm.scopus.merged$N, sm.scopus.merged$Documents, use ="complete.obs", method = "spearman")

@@

title <- sm.df %>% arrange(desc(Overall.N)) %>% distinct(title)
title.order <- title$title
sm.df$title2 <- factor(sm.df$title, levels = (title.order))
Overall.N <- distinct(sm.df, title)

@@

sm.scopus.merged.3 <- sm.scopus.merged %>% group_by(Year) %>%
    mutate(HD.N = sum(N))

sm.scopus.merged.4 <- sm.scopus.merged %>% select(Year, Documents)

sm.scopus.merged.4 <- na.omit(sm.scopus.merged.4)
sm.scopus.merged.4 <- sm.scopus.merged.4 %>% group_by(Year) %>% mutate(scopus.N = sum(Documents))

ggplot(sm.scopus.merged.3, aes(Year, HD.N), group=1) + geom_line() +
    geom_line(data =sm.scopus.merged.4, aes(Year, scopus.N), colour = "red")
